Quality Definitions of Qualities

### 2019-11-06 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Reformated Reliability to use definition environments

\begin{itemize}
\item{Definition 1:} The probability that the software will operate as expected
  over a specified time interval (\cite{GhezziEtAl2003}).
\item{Definition 2:} A set of attributes that relate to the capability of
  software to maintain its level of performance under stated conditions for a
  stated period of time (\cite{berander2005software}).
\item{Definition 3:} “The capability of the software product to maintain a
  specified level of performance when used under specified conditions
  (\cite{international2001iso}).
\item{Definition 4:} Code possesses the characteristic reliability to the extent
  that it can be expected to perform its intended functions satisfactorily
  (\cite{boehm2007software})
\item{Definition 5:} A concern encompassing correctness and robustness
  (\cite{meyer1988object}).
\end{itemize}

>>>>

\begin{defn}
  The probability that the software will operate as expected over a specified
  time interval (\cite{GhezziEtAl2003}).
\end{defn}

\begin{defn}
  A set of attributes that relate to the capability of software to maintain its
  level of performance under stated conditions for a stated period of time
  (\cite{berander2005software}).
\end{defn}

\begin{defn}
  ``The capability of the software product to maintain a specified level of
  performance when used under specified conditions''
  (\cite{international2001iso}).
\end{defn}

\begin{defn}
  Code possesses the characteristic reliability to the extent that it can be
  expected to perform its intended functions satisfactorily
  (\cite{boehm2007software}).
\end{defn}

\begin{defn}
  A concern encompassing correctness and robustness (\cite{meyer1988object}).
\end{defn}
